MultiDataProcessPico

### 2023-12-07 Code/MultiDataProcessPico.Rmd
Fixed file path in ProcessPico rmd

## Set figure caption font size
```{css, echo=FALSE}
p.caption {
  font-size: 18px;
}
```

@@

```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
#library(tidyquant)
#library(data.table)
#library(googledrive)
#library(googlesheets4)
library(minpack.lm)
#library(dplyr)

#attach psych for harmonic.mean() for averaging rates
#library(psych)
#library(RcppRoll) #replaced by zoo::rollmean for rolling mean consistent with MultiDataImportPico.Rmd usage

@@

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("ImportedData")
PlotsPath <- file.path("..","Plots")
DataOut <- file.path("ProcessedData", "MultiCultiData")

@@

GrowthFlagError <- 0.20 # percentage of growth parameter is flagged as growth when std error is less than xx of mu .

Sensor <- "od-680"

@@

#set the hour of day at which photoperiod starts for later generation of ToD Time of Day
#replaced by extraction of StartHour from first row of data file in MultiDataImport.Rmd
#StartHour <- 6
#EndHour <- 18

@@

```{r set colours}
MyWavelengths = c(405, 450, 470, 530, 620, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")

@@

Moving this template to a working project folder will need editing of this file path to a relative path within the project folder.
```{r read ProcessFile}
ProcessFile <- "ImportedData/20220929_PICO_MCMIX006_RUN92_TargetDataMetaFilter.Rds"

ProcessFileName <- str_split(string = ProcessFile, "/")[[1]][2] %>%
  str_remove(pattern = ".Rds") %>%
  str_remove(pattern = "_TargetDataMetaFilter")
ProcessFileName

@@

```{r filter }
ProcessDataNestGrowth <- ProcessDataNestGrowth %>% 
  select(-contains(c("trunc", "Gompertz", "Gomp", "OD720_G", "deltaOD_G")))
```

@@

# #predictions of condition specific fits
OD720LogGrowthPlot <-ProcessDataNestGrowth %>%
#drop_na(OD720_logistic) %>%
  mutate(OD720_logistic_predict = map(OD720_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, OD720_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_OD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.resid), colour = "gold", size = 0.05) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
#scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "OD720 Logistic:  Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

OD720LogGrowthPlot

deltaODLogGrowthPlot <- ProcessDataNestGrowth %>%
  mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "DeltaOD Logistic:   Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

deltaODLogGrowthPlot

@@

lognormOD720GompertzGrowthPlot <- ProcessDataNestGrowth %>%
  mutate(lognormOD720_Gompertz_predict = map(lognormOD720_Gompertz, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, lognormOD720_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_lognormOD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.resid), colour = "gold", size = 0.05) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "lognormOD720_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormOD720", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+ 
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

lognormOD720GompertzGrowthPlot

ProcessDataNestGrowth %>%
  filter(Tube == 5) %>%
  mutate(lognormOD720_Gompertz_predict = map(lognormOD720_Gompertz, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, lognormOD720_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_lognormOD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.resid), colour = "gold", size = 0.05) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "lognormOD720_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormOD720", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+ 
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

lognormdeltaODGompertzGrowthPlot <- ProcessDataNestGrowth %>%
  mutate(lognormdeltaOD_Gompertz_predict = map(lognormdeltaOD_Gompertz, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, lognormdeltaOD_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_lognormdeltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.resid), colour = "gold", size = 0.05) +geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "lognormdeltaOD_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormdeltaOD", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+ 
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

lognormdeltaODGompertzGrowthPlot

ProcessDataNestGrowth %>%
  filter(Tube == 2) %>%
  mutate(lognormdeltaOD_Gompertz_predict = map(lognormdeltaOD_Gompertz, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, lognormdeltaOD_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_lognormdeltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.resid), colour = "gold", size = 0.05) +geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "lognormdeltaOD_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormdeltaOD", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+ 
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

ProcessDataNestGrowth %>%
  filter(Tube == 5) %>%
  mutate(PhotoperiodLabel = "Photoperiod",
         OxygenLabel = "Oxygen level") %>% 
  mutate(lognormdeltaOD_Gompertz_predict = map(lognormdeltaOD_Gompertz, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, lognormdeltaOD_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_lognormdeltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.resid), colour = "gold", size = 0.05) +geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
   facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
 # guides(fill = "none") +
  labs(subtitle = "lognormdeltaOD_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormdeltaOD", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+ 
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

```{r save logistic model plots}
# ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "OD720LogGrowthPlot",".png",sep = "")), plot = OD720LogGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "deltaODLogGrowthPlot",".png",sep = "")), plot = deltaODLogGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)

 # ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "OD720LogGrowthPlotExpand",".png",sep = "")), plot = OD720LogGrowthPlotExpand, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
#

 # ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "DeltaODLogGrowthPlotExpand",".png",sep = "")), plot = DeltaODLogGrowthPlotExpand, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)

 # ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "lognormOD720GompertzGrowthPlot",".png",sep = "")), plot = lognormOD720GompertzGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
 # 
 #  ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "lognormdeltaODGompertzGrowthPlot",".png",sep = "")), plot = lognormdeltaODGompertzGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

```{r logistic vs gompertz fit plots}

ProcessDataNestGrowth %>%
unnest(cols = c(OD720_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error, OD720_logistic_tidied_statistic, OD720_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept)  %>%
  unnest(cols = c(lognormOD720_Gompertz_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error, lognormOD720_Gompertz_tidied_statistic, lognormOD720_Gompertz_tidied_p.value), names_sep = "_") %>%
  rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
         OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
         OD720_Gmu = lognormOD720_Gompertz_tidied_estimate_Gmu,
         OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
         OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,             
         OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag)  %>%
   ggplot() +
  geom_point(aes(x = OD720_Lmu, y = OD720_Gmu, colour = as.factor(WL),  shape = as.factor(IsOD720_GLagNeg)), size = 4)  +
  ggrepel::geom_text_repel(aes(x = OD720_Lmu, y = OD720_Gmu, label= Tube),hjust=0, vjust=0) +
scale_colour_manual(values = MCMIXColours) +
  scale_shape_manual(values = c(13, 16)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1) +
  coord_cartesian(xlim = c (0, 0.06), ylim = c(0, 0.06)) +
  scale_x_continuous(breaks=seq(0, 0.06, by = 0.02)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Gompertz Growth Rate (OD720_Gmu)", x = "Logistic Growth Rate (OD720_Lmu)") +
  facet_grid(rows = vars(Strain), cols = vars(O2, WL)) + 
  theme_bw() + 
  labs(title = "Logistic vs. Gompertz Cell Specific Growth Rates (µ" ~ h^-1~")- All Growth",
       colour = "Actinic PAR (nm)")

ProcessDataNestGrowth %>%
unnest(cols = c(deltaOD_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error, deltaOD_logistic_tidied_statistic, deltaOD_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept)  %>%
  unnest(cols = c(lognormdeltaOD_Gompertz_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error, lognormdeltaOD_Gompertz_tidied_statistic, lognormdeltaOD_Gompertz_tidied_p.value), names_sep = "_") %>%
  rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
         deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
         deltaOD_Gmu = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
         deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
         deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,             
         deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag)  %>%
   ggplot() +
  geom_point(aes(x = deltaOD_Lmu, y = deltaOD_Gmu, colour = as.factor(WL),  shape = as.factor(IsdeltaOD_GLagNeg)), size = 4) +
  ggrepel::geom_text_repel(aes(x = deltaOD_Lmu, y = deltaOD_Gmu, label= Tube),hjust=0, vjust=0) +
scale_colour_manual(values = MCMIXColours) +
  scale_shape_manual(values = c(13, 16)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1) +
  coord_cartesian(xlim = c (0, 0.06), ylim = c(0, 0.06)) +
  scale_x_continuous(breaks=seq(0, 0.06, by = 0.02)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Gompertz Growth Rate (deltaOD_Gmu)", x = "Logistic Growth Rate (deltaOD_Lmu)") +
  facet_grid(rows = vars(Strain), cols = vars(O2, WL)) + 
  theme_bw() + 
  labs(title = "Logistic vs. Gompertz Chlorophyll Specific Growth Rates (µ" ~ h^-1~")- All Growth",
       colour = "Actinic PAR (nm)")

@@

Plot Fit Terms vs. conditions - High Std error filtered out by flag argument
```{r logistic fit terms plot}
ProcessDataNestGrowth %>%
 unnest(cols = c(OD720_logistic_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, OD720_logistic_tidied_term, OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error)) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error), names_sep = "_") %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept) %>%
  mutate(LmuOD720Flag = if_else(OD720_Lmu_se < OD720_Lmu * GrowthFlagError, 1, 0)) %>%
# mutate(GrowthFlag = if_else((OD720_Lintercept + OD720_Lintercept_se) < ((OD720_Lmax - OD720_Lmax_se) & (OD720_Lmu_se < OD720_Lmu * GrowthFlagError) & (OD720_Lmax_se < OD720_Lmax * GrowthFlagError) ), 1, 0)) %>%
  filter(LmuOD720Flag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = OD720_Lmu, colour = as.factor(WL))) +
  geom_errorbar(aes(x = Par_ue, ymin = OD720_Lmu - OD720_Lmu_se, ymax = OD720_Lmu + OD720_Lmu_se, colour = as.factor(WL))) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Logistic cell Specific Growth rates - Flagged High Std error Omitted")

ProcessDataNestGrowth %>%
 unnest(cols = c(deltaOD_logistic_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, deltaOD_logistic_tidied_term, deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error)) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error), names_sep = "_") %>%
  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept) %>%
  mutate(LmudeltaODFlag = if_else(deltaOD_Lmu_se < deltaOD_Lmu * GrowthFlagError, 1, 0)) %>%
 # mutate(GrowthFlag = if_else((deltaOD_Lintercept + deltaOD_Lintercept_se) < ((deltaOD_Lmax - deltaOD_Lmax_se) & (deltaOD_Lmu_se < deltaOD_Lmu * GrowthFlagError) & (deltaOD_Lmax_se < deltaOD_Lmax * GrowthFlagError) ), 1, 0)) %>%
  filter(LmudeltaODFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu, colour = as.factor(WL))) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu - deltaOD_Lmu_se, ymax = deltaOD_Lmu + deltaOD_Lmu_se, colour = as.factor(WL))) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Logistic chlorophyll specific - Flagged High Std error Omitted")

>>>>

@@

```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
library(minpack.lm)
library(photobiologyWavebands)

@@

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "ImportedData", "MultiCultiData")
DataOut <- file.path("..", "Data","ProcessedData", "MultiCultiData")

@@

GrowthFlagError <- 0.20 # percentage of growth parameter is flagged as growth when std error is less than xx of mu.

@@

@@

```{r set colours}
MyWavelengths = c(405, 445, 470, 530, 620, 660, 730, "WW")
MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530),            w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))

@@

Moving this template to a working project folder will need editing of this file path to a relative path within the project folder.
```{r read ProcessFile}
ProcessFile <- "../Data/ImportedData/MultiCultiData/20211223_PICO_MCMIX006_RUN42_TargetDataMetaFilter.Rds"

ProcessFileName <- str_split(string = ProcessFile, "/")[[1]][5] %>%
  str_remove(pattern = ".Rds") %>%
  str_remove(pattern = "_TargetDataMetaFilter")

ProcessFileName

@@

@@

# #predictions of condition specific fits
ProcessDataNestGrowth %>%
#drop_na(OD720_logistic) %>%
  mutate(OD720_logistic_predict = map(OD720_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, OD720_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_OD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.resid), colour = "gold", size = 0.05) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
#scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "OD720 Logistic:  Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

ProcessDataNestGrowth %>%
  mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "DeltaOD Logistic:   Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

@@

@@

@@

Plot Fit Terms vs. conditions - High Std error filtered out by flag argument
```{r logistic fit terms plot}
ProcessDataNestGrowth %>%
 unnest(cols = c(OD720_logistic_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, OD720_logistic_tidied_term, OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error)) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error), names_sep = "_") %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept) %>%
  mutate(LmuOD720Flag = if_else(OD720_Lmu_se < OD720_Lmu * GrowthFlagError, 1, 0)) %>%
# mutate(GrowthFlag = if_else((OD720_Lintercept + OD720_Lintercept_se) < ((OD720_Lmax - OD720_Lmax_se) & (OD720_Lmu_se < OD720_Lmu * GrowthFlagError) & (OD720_Lmax_se < OD720_Lmax * GrowthFlagError) ), 1, 0)) %>%
  filter(LmuOD720Flag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = OD720_Lmu, colour = as.factor(WL))) +
  geom_errorbar(aes(x = Par_ue, ymin = OD720_Lmu - OD720_Lmu_se, ymax = OD720_Lmu + OD720_Lmu_se, colour = as.factor(WL))) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Logistic cell scatter growth rates - High std error fits omitted")

ProcessDataNestGrowth %>%
 unnest(cols = c(deltaOD_logistic_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, deltaOD_logistic_tidied_term, deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error)) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error), names_sep = "_") %>%
  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept) %>%
  mutate(LmudeltaODFlag = if_else(deltaOD_Lmu_se < deltaOD_Lmu * GrowthFlagError, 1, 0)) %>%
 # mutate(GrowthFlag = if_else((deltaOD_Lintercept + deltaOD_Lintercept_se) < ((deltaOD_Lmax - deltaOD_Lmax_se) & (deltaOD_Lmu_se < deltaOD_Lmu * GrowthFlagError) & (deltaOD_Lmax_se < deltaOD_Lmax * GrowthFlagError) ), 1, 0)) %>%
  filter(LmudeltaODFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu, colour = as.factor(WL))) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu - deltaOD_Lmu_se, ymax = deltaOD_Lmu + deltaOD_Lmu_se, colour = as.factor(WL))) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Logistic chlorophyll specific growth rates - High Std error fits omitted")
